\par After five and a half years of ups and downs, I would like to express my 
gratitude to those people and organizations that have contributed to my 
success in completing this thesis. 

\par First on the list is the Physics Department at the University of 
Texas at Arlington for providing an environment conducive to academic learning and 
growth. The personal and academic growth that I have enjoyed could not have been 
possible without direct mentorship from Dr. Jaehoon Yu, my supervising professor. 
I feel a similar sentiment towards all the help that I got from Dr. Justin Griffiths, 
who taught me most of what I know about computer programming.  

\par I would also like to thank Amon and Enery, my parents, for supporting me in 
my decision to pursue higher education and for all the patience that came along with 
that decision. The same goes for my brothers John and Steven, and my sisters Ellen and 
Rachel. My wife Andrea's ability to cope with my grumpiness during my downs has 
been unparalleled; a lot of credit goes to her.

\par The list of friends that have helped me is endless. To name a few, Marshall Ndhlovu, 
Tatenda Yemeke, Nancy Kasvosve, Simba Gandari, and Joshua Rutanhira. I would like to express my gratitude 
to them.  

%\par Lastly, Argonne National Laboratory, Brookhaven National Laboratory and CERN all 
%deserve an honorable mention for providing the ideal tools for conducting my research.
%I would also like to thank all other people that have provided me assistance in 
%any way.    
