I would like to thank my supervising professor Dr. Vasant Prabhu for constantly motivating
and encouraging me, and also for his invaluable advice during the course of my doctoral studies.
I wish to thank my academic advisors Dr. Jonathan Bredow, Dr. Chien-Pai Han, Dr. Harold Sobol,
Dr. Saibun Tjuatja and Dr. Stone Tseng for their interest in my research and for taking time to
serve in my dissertation committee.\\

I would also like to extend my appreciation to Nortel Networks for providing
financial support for my doctoral studies. I wish to thank Meng Yee, Robert Hunt and
Dr. Michael Maragoudakis with Wireless Network Engineering for their support and encouragement.
I am especially grateful to Mazin Al-Shalash for  his interest in my research and for the helpful
discussions and invaluable comments. I wish also to thank Dr. Yaser Ibrahim, Dr. Mini Vassudevan and
Kal Mustafa for taking the time to critically evaluate this manuscript.\\

I am grateful to all the teachers who taught me during the years I spent in school, first
in Palestine, then in Iraq and finally in the Unites States. I would like to thank Dr. Saleh Al-Araji
for encouraging and inspiring me to pursue graduate studies.\\


Finally, I would like to express my deep gratitude to my brothers
who have encouraged and inspired me and sponsored my undergraduate
and graduate studies. I am extremely fortunate to be so blessed. I
am also extremely grateful to my mother, sister and wife for their
sacrifice, encouragement and patience. I also thank several of my
friends who have helped me throughout my career.
