\chapter{ATLAS Simulation Chain}
\begin{chapabstract}
\par Simulations are widely used to predict rates of physics processes and their kinematic properties. 
Within ATLAS, Monte Carlo methods are the simulation of choice. The process of producing the simulation 
data is referred to in this Chapter as the `ATLAS Simulation Chain'. This chain essentially comprises three 
stages. First is the `Event Generation', during which $pp$ collisions are simulated and physics processes at 
a high energy scale are generated. In addition, parton showers and subsequent hadronizations are simulated. 
Second is the `Detector Simulation', during which the particle traversal in the ATLAS detector is simulated.
During `Digitization', detector simulation output is converted to `digits'. The digitized simulation 
data is eventually passed through the standard ATLAS Trigger system and saved on disk just like real data.      

\par This chapter is divided into two sections. Event generation is discussed in Section~\ref{sec:evgen}. 
Here, cross section for physics processes is formulated, the parton shower is developed, and hadronization 
models are presented. In addition, Monte Carlo generators used in this thesis are presented. Section~\ref{sec:detsim} 
discussed the ATLAS detector simulation and the subsequent treatment of simulation data.  
\end{chapabstract}
\label{sim}

\section{Event Generation}
\label{sec:evgen}
\input{sections/evgen.tex}

\section{Detector Simulation and Data Management}
\label{sec:detsim}
\input{sections/detsim.tex}

%\begin{chapsummary}
%\par The ATLAS Simulation chain was presented in this Chapter. Models for hard scattering, 
%parton showering and hadronizations were also presented. Several Monte Carlo generators that 
%implement these models were outlined. Such implementations are such that particular generators 
%work best for modelling specific physics processes. Simulation of particle traversal in the ATLAS 
%detector through GEANT4 was discussed. Both Fast and Full simulation techniques were presented. 
%Finally, simulation data treatment after the simulation chain was discussed and shown to be almost identical 
%to treatment of real data save for a few details in the triggering system.  
%\end{chapsummary}
