\chapter{Exclusive Higgs Search}
\label{exclH}
\begin{chapabstract}
A search for evidence of the exclusively produced SM Higgs boson from LHC collisions is 
presented in this chapter. The only mass probed was 125~\GeV\ for the SM Higgs boson.
Exclusion limits were 
set on the total production cross section of the exclusive SM 
Higgs boson.  
In Section~\ref{sec:dataSimExclH} the data-sets used in the search are presented. Data obtained from 
LHC collisions is referred to as {\it data}, while data obtained from simulation is just referred to 
as {\it simulation}. In Section~\ref{sec:objExclH} physics object selection criteria are presented, adding to the 
 criteria presented in Chapter~\ref{obj}. In Section~\ref{sec:selExclH} the 
criteria to select events with a charged Higgs boson 
signature are introduced. Treatment of backgrounds to the charged Higgs boson is discussed in 
Section~\ref{sec:bkgExclH}, with the associated systematic uncertainties discussed in Section~\ref{sec:exclHUnc}. 
Final event yields are presented in Section~\ref{sec:exclHres}, and their statistical assessment is 
discussed in the same section.
\end{chapabstract}

\section{Data and Simulation}
\label{sec:dataSimExclH}
\input{sections/mcExclH.tex}

\section{Object Selection}
\label{sec:objExclH}
\input{sections/objExclH.tex}

\section{Event Selection}
\label{sec:selExclH}
\input{sections/exclHSel.tex}

\section{Modelling of background processes}
\label{sec:bkgExclH}
\input{sections/exclHBkg.tex}

\section{Validation of background modelling}
\label{sec:exclHCR}
\par The section discusses validation of background modelling. Two regions in data were 
defined to validate modelling of exclusive and inclusive backgrounds. 

\par Since the major 
exclusive background is exclusive \WW, a region that enhanced such events is discussed here. 
This region also contains a significant contribution from inclusive \WW, so it demonstrates the 
validity of the inclusive \WW\ modelling techniques discussed in the preceding sections. 

\par Although \Ztau\ events were not expected to be very significant in the signal region, 
studying background composition in a region of data rich in \Ztau\ events reinforced that 
all the other backgrounds were reasonably well-modelled. 

\input{sections/exclHCR.tex}

\section{Systematic Uncertainties and Statistical analysis}
\label{sec:exclHUnc}
\input{sections/exclHunc.tex}

\section{Results}
\label{sec:exclHres}
\input{sections/exclHres.tex}


%
%\begin{chapsummary}
%\par A search for evidence of the exclusive Higgs boson in LHC's Run I data-set was performed, 
%in the channel where the Higgs boson decays to a pair of \Wpm\ which subsequently decay 
%leptonically. Decay of \Wpm\ to $\tau$ leptons were allowed only if the $\tau$ lepton 
%decayed leptonically. A new method for separating exclusive events from inclusive events was devised, specifically for 
%isolating exclusive Higgs events. This method was tested in both simulation and data, correcting any mis-modelling 
%observed in simulation. Overall, background treatment was validated in two regions of data and observed to 
%be reasonable. In the signal region, six events were observed in data while 3.00$\pm$0.78 events were expected from all 
%the background processes. This discrepancy was evaluated to be 1.1$\sigma$ higher than expected, and hence 
%not high enough to conclude the presence of exclusive Higgs events in the data-set. Upper limits were therefore 
%set on the total production cross section of the exclusive Higgs boson. The set limits were 400 times 
%the cross section predicted by the most popular model for the production of the exclusive Higgs boson.  
%\end{chapsummary}
