\chapter{Physics Objects}
\begin{chapabstract}
The link between the particles introduced in Chapter~\ref{theory} and the experimental setup introduced in 
Chapter~\ref{expSetup} is established in this chapter. The signatures printed by these particles in 
the ATLAS detector are referred to here collectively as {\it physics objects}. Dedicated algorithms are used to 
{\it reconstructed} these physics objects from detector electrical signals. In some cases, other algorithms are used to 
further {\it identify} the physics objects from the reconstructed objects. Reconstruction and identification
procedures are described in this chapter in detail for each of the physics objects used in analyses discussed 
in Chapters~\ref{chargedH} and \ref{exclH}. Photons were not directly used in either 
analysis, so their reconstruction and identification are not discussed here. Rather, sufficient references are supplied.   
\end{chapabstract}
\label{obj}

	\section{Tracks}
	\label{sec:tracking}
\par As explained in Chapter~\ref{expSetup}, charged particles leave traces that describe 
their traversal paths in the ATLAS detector's Inner Detector (ID) and the Muon Spectrometer (MS).
These traces are known as {\it tracks}, and the methodology of recording these tracks 
is referred to as {\it tracking}. In Sections~\ref{sec:ID}
 and \ref{sec:muonSpec}, it was shown that the MS exclusively tracks muons 
while the ID tracks any charged particles. Because of this difference in purpose, 
different approaches are taken when reconstructing tracks in the MS and ID. 
Since any relatively long-lived charged particles leave tracks in the ID, no 
separate identification schemes are applied to identify tracks in their own right. 
This section discusses tracking systems in the ID and MS. 
 
\input{sections/tracking.tex}
	
	\section{Electrons}
	\label{sec:ele}
\input{sections/electrons.tex}	

	\section{Muons}
	\label{sec:mu}
\input{sections/muons.tex}

	\section{Jets}
	\label{sec:jets}
\input{sections/jets.tex}

	\section{Taus}
	\label{sec:tau}
\par As discussed in Section~\ref{sec:sm}, of all leptons the $\tau$ lepton has the smallest 
mean lifetime of \SI{2.9e-13}{\s} ($c\tau \approx \SI{87}{\micron}$), 
decaying inside the LHC beam pipe.\footnote{The LHC beam pipe has 
an external diameter of about 5.3~cm.}
Also the heaviest of all the leptons, the $\tau$ lepton is the only lepton 
heavy enough to decay to hadrons, with a branching ratio of approximately 
65\%. The said hadrons are dominated by neutral and charged pions, although 2.7\% of the 
time the $\tau$ lepton decays to kaons. 

\input{sections/taus.tex}

	\section{Missing Energy}
	\label{sec:met}
\input{sections/met.tex}

%\begin{chapsummary}
%Reconstruction of physics objects that are later used in Chapters~\ref{chargedH} and \ref{exclH} from the 
%ATLAS detector signals was discussed in this chapter. Photons were not discussed, but references were supplied. 
%Modelling of these reconstruction and identification schemes in Monte Carlo simulation was described, discussing any 
%necessary corrections that were applied. Evaluation of systematic uncertainties on each of these schemes was outlined, and 
%the sizes of the uncertainties were given.  
%\end{chapsummary}
