\chapter{Theoretical Framework}
\begin{chapabstract}
\par A theoretical framework for elementary particles is introduced and discussed 
in detail in this chapter, in the form of the Standard Model (SM).
Fundamental particles that the SM predicts are presented, along with their quantum numbers and other properties. 
SM is formally constructed from concepts borrowed from relativistic and quantum theories.  
Motivation for the existence of a neutral Higgs boson is introduced from  
spontaneous symmetry breaking. Supersymmetry is presented as a possible solution to one of the 
hierarchy problem. Through this lens, a family of Higgs bosons is presented in 
the Two-Higgs Doblet Model (2HDM), an extension of the Standard Model; 
the charged Higgs boson (\Hpm) is presented as a member of this family. 
Finally, diffractive production\footnote{Diffractive production is also referred to as 
exclusive production in this thesis.} of the neutral SM Higgs is explored in the context of 
proton-proton scattering experiments.  
\end{chapabstract}
\label{theory}

\section{The Standard Model}
\label{sec:sm}
\input{sections/sm.tex}

\section{Exclusive Particle Interactions}
\label{sec:diffPhy}
\input{sections/diffOverview.tex}
\input{sections/diffPhys.tex} 

\section{Minimal Supersymmetric Standard Model} 
\label{sec:twohdm}
\par The hierarchy problem alluded to in Chapter~\ref{intro} induces a discrepancy in the predicted 
and observed Higgs boson masses. To match the observed Higgs mass, the SM has to be fine-tuned by 
subtracting semi-divergent terms from the Lagrangian. To reduce this fine-tuning, the 
Minimal Supersymmetric Standard Model (MSSM)~\cite{FAYET1976159} postulates that for each particle predicted by the SM 
there exists a super-partner with different quantum numbers. Adding such particles does 
reduce the level of fine-tuning required on the SM and moderates corrections to the 
Higgs mass. In this framework, the Higgs boson becomes a member of a family of Higgs 
bosons, and is referred to as $h$.\footnote{In 
preceding sections $h$ was represented by $H$. Apologies for the expected 
confusion.} In this specification, MSSM is referred to as hMSSM~\cite{Djouadi:2013uqa}.
In addition to $h$, hMSSM predicts 4 more Higgs bosons: two 
charged $H^{\pm}$, one CP-even $H$, and one CP-odd $A$. 
 
\input{sections/twohdm.tex}
\input{sections/chargedHiggs.tex}

%\begin{chapsummary}
%\par The Standard Model was presented in this chapter. First its predictions, which provide 
%the fundamental particles of nature, were outlined. Its successes and failures were outlined.
% The Standard Model was then built 
%using concepts from group theory, relativity and quantum theory. Among the Standard 
%Model predictions is the Higgs boson. Its couplings to other fundamental particles was discussed. 
%Its production in diffractive processes, in the context of proton collisions, was discussed through other models external to 
%the Standard Model, prompting motivation for one part of this thesis. The Minimal Supersymmetric Standard Model (MSSM) was introduced as a proposed 
%solution to the hierarchy problem, which the Standard Model fails to fix.  
%The MSSM predictions, such as the charged Higgs boson, were discussed. 
%The charged Higgs boson coupling to fundamental particles in the Standard Model was also outlined, 
%prompting motivation for the second part of this thesis.  
%\end{chapsummary}
